### 2022-04-29 dev/submissions/aies/sections/support.qmd
Fun with latex templates

@@

Patrick has been my supervisee for ...

>>>>

---
format:
    pdf: default
---

@@

As substantiated in more detail in my full letter of support (attached with this application), as Patrick's advisor, I am very happy to support his application to the AIES student track. Patrick is an eager student, with a pro-active enthusiasm to learn from others, and contribute himself to the learning progress of relevant communities. Getting him to present at AIES will be very valuable for receiving feedback on his current work, while I would more broadly be happy to receive the community's guidance on how to best navigate questions of ethics and responsibility in a project like his. In case of a positive outcome of this application, we are in a position to fully cover Patrick's costs, and thus will not lay any claim on the financial waivers.
